#Load in the data and packages!
```{R}
library(haven)
library(ggplot2)
library(flexplot)
library(tidyr)
library(lme4)
library(dplyr)
library(knitr)
library(flextable)
library(officer)
library(webshot2)
library(apaTables)
df <- read_sav('P6003.A4.sav')
```

#Data Exploration
```{R}
#Exploring what our data looks like utilizing flexplot distributions. 
flexplot(swl ~ 1, data = df)           #swl - Satisfaction with life
flexplot(tipm.E ~ 1, data = df)        #tipm.E - Extraversion
flexplot(tipm.N ~ 1, data = df)        #tipm.N - Neuroticism

correlation <- cor(df$tipm.E, df$tipm.N, use = "complete.obs", method = "spearman")
print(correlation) #No outliers or anything extreme. Our two predictors are also not highly correlated!
```


#Descriptive Statistics Table Creation
```{r}

df_summary <- df %>%                                              
  summarise(across(c('swl', 'tipm.E', 'tipm.N'),         #Summarize lets us get the mean/sd of our three variables
                   list(Mean = ~mean(.x, na.rm = TRUE), 
                        SD = ~sd(.x, na.rm = TRUE)))) %>%
  pivot_longer(cols = everything(),          #Using pivot longer and wider we can make a 3x6 dataframe of our summary
               names_to = c("Variable", "Statistic"),
               names_sep = "_") %>%
  pivot_wider(names_from = Statistic, values_from = value) %>%  #Now pivot wider lets us make a 2x3 df of our summary                                                                  based on similar names in statistic and value columns. 
  mutate(across(c(Mean, SD), ~round(.x, 2)))                    #Ensure rounding

df_summary$Variable <- recode(df_summary$Variable,         #Rename our variable so its clear on the APA table. 
                              "swl" = "SWL",
                              "tipm.E" = "Extraversion",
                              "tipm.N" = "Neuroticism")

apa_table <- flextable(df_summary) %>%                #Use flextable to create apa style table. 
  theme_booktabs() %>%
  set_caption("Table 1: Descriptive Statistics") %>%
  colformat_double(j = 2:3, digits = 2) %>%
  align(j = 2:3, align = "center") %>%
  width(j = 1, width = 2) %>%
  autofit()

print(apa_table)               
save_as_image(apa_table, path = "apa_table_descriptions.png")     #Saving it as a PNG to put in our paper later!
```

#Correlation Table
```{r}
apa.cor.table(df %>% select(tipm.E, tipm.N, swl), 
              filename = "correlation_table.doc", 
              show.sig.stars = TRUE)
```

#Before moving to analysis, plotting residuals of our model to test for assumptions utilizing flexplot for each of our hypothesises
```{R}
hypoglm1 <- glm(swl ~ tipm.E, data = df)
visualize(hypoglm1, plot="residuals")
hypoglm2 <- glm(swl ~ tipm.N, data = df)
visualize(hypoglm2, plot="residuals")
hypoglm3.1 <- glm(swl ~ tipm.E*day, data = df)
visualize(hypoglm3, plot="residuals")
hypoglm3.2 <- glm(swl ~ tipm.N*day, data = df)
visualize(hypoglm3, plot="residuals")
```
##We have a big issue! There is not consistency of variance for any residuals! Variance is also not extremely normal but it's okay. We believe that having multiple testing from ID is likely explaining the issue with the plots. 

##Let's make a graph to visualize this.
##Using head, we se tha tthe dataframe is oragnized by participant ID. This makes the next part easier
##We use head to take the top 500 observations 
##We then graph id on the x axis and y axis for satisfiaction with life, to see if different ID's have different SWL's or if theya re similar.

```{R}
head(df, 10)
dfexamine <- head(df, 500)

ggplot(dfexamine, aes(x = factor(id), y = swl)) + 
  geom_boxplot() + 
  theme_classic()
```

#This visual exploration shows that satisfaciton with life is not independent from ID, meaning that ID is impacting SWL. This means we are going to need a random effect due to there being repeated observations for our model. 



##Let's see how mcuh adding a random fixed intercept explains our outcome of satiance, using lmer and having 1+(1|id) we are purely looking at how much a specific person's multiple observation explains the variance. 
```{R}
baseline <- lmer(swl ~ 1+(1|id), data = df, REML = FALSE)
summary(baseline)
icc(baseline)   ##An ICC of 0.74 implies that ID explains about 74% of our variance, which means that we will need some                   random effects for id!
```

#Hypothesis 1 + 2
```{R}
#First model for Hypothesis 1: Fixed effect tipm.E and a random intercept for ID. Outcome is SWL. 
hypo1.2.a <- lmer(swl ~ tipm.E +  tipm.N + (1|id), data = df, REML = FALSE)
visualize(hypo1.2.a, plot = 'residuals')             #Visualization reveals that we do not have constant variance.                                                           In addition a random slope could be added to this model to                                                             increase fit
```

#Alternative Model for Hypothesis 1, model comparison, and visualization of new model. 
```{R}
#Alternative Model for Hypothesis 1: Fixed effect tipm.E. Random slope for tipm.E and random intercept for ID. Outcome is SWL. 
hypo1.2.b <- lmer(swl ~ tipm.E + tipm.N + (1 + tipm.N + tipm.E|id), data = df, REML = FALSE)

#Model Comparison
model.comparison(hypo1.2.a, hypo1.2.b)

#The model comparison we get is very significant! Adding a random slope for tipm.e does appear to explain more variance based on the lower AIC, lower BIC, larger bayes.factor, and significant P.

#Visualization of Results
visualize(hypo1.2.b, plot = 'residuals')  

#It looks like even though the new model has a better fit, it still is breaking constantly variance. This means our model is breaking some assumptions but we will simply state this and move onto to our new hypothesis. 
summary(hypo1.2.b)
```



#Hypothesis 3a: Effect of time on tipm.E
```{r}
#First Model for Hypo 3a: Effect of Overtime on tipm.E.  
hypo1.2.b <- lmer(swl ~ tipm.E + tipm.N + (1 + tipm.N + tipm.E|id), data = df, REML = FALSE)

hypo3ab <- lmer(swl ~ tipm.E + tipm.N + tipm.E*day + tipm.N*day + (1 + tipm.N + tipm.E|id), data = df, REML = FALSE)

model.comparison (hypo1.2.b, hypo3ab)
summary(hypo3ac)
```

```{r}
summary(hypo3ab)
visualize(hypo3ab, plot = 'residuals')
visualize(hypo3ab)
```
